Verifying Demonstrations

### 2021-06-15 paper/verifiability-analysis.tex
Clarifies confusion about trust in security analysis

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed at the location when the proof share was created.
In essence, the witness performs distance bounding to ensure Alice is close to 
them, this is then propagated to the verifier through the signature and founded 
on trust (remember that the witness is trusted by the verifier).
Alice has three options:
\begin{enumerate*}
\item\label{spatial-DF} relay her communication with an honest witness through 
  a conspirator,
\item\label{spatial-forge} forge a witness signature for the proof,
\item corrupt a witness to issue a proof although neither might be present at 
  the location.
\end{enumerate*}

>>>>

\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
indeed at the location when the proof share was created.
In essence, the witness performs distance bounding to ensure Alice is close to 
them, this is then propagated to the verifier through the signature.
This leaves Alice with three options to cheat:
\begin{enumerate*}
\item\label{spatial-DF} relay her communication with an honest witness through 
  a conspirator,
\item\label{spatial-forge} forge a witness signature for the proof,
\item corrupt a witness to issue a proof although neither might be present at 
  the location.
\end{enumerate*}
